Due to the radiological risk of tritium, it is important that the current legislation limit the release of tritium to the environment ensuring that the levels are below a safe value for public health.

The guidelines to limit the radioactive elements in drinking water for many countries are based on the radiation protection methodology developed by the ICRP \cite{ICRP_GL} and the recommendations from WHO \cite{WHO_GL}. The objective of the international radiation methodology is to  protect people and the environment from the negative effects of ionising radiations but allowing beneficial activities that involve a reasonable radiation exposure. This is based on three main points, which are:
\begin{enumerate}
\item{} The justification: The benefit from radiological exposure must outweigh the detriment to health that it causes.
\item{} The ALARA principle ("As Low As Reasonably Achievable"): The radiological exposure must be kept as low as possible considering social and economic factors.
\item{} The dose limitation: Limit that must never be exceeded.
\end{enumerate}

While the ICRP recommends a maximum dose of $1~\milli\sievert/$yr, excluding the natural background and medical interventions, the WHO is more conservative, recommending a maximum dose of $0.1~\milli\sievert/$yr, which corresponds to less than $5\%$ of the annual dose due to background radiation, $2.42~\milli\sievert/$year. The guideline reference level of each radionuclide in drinking water, GL, is usually calculated from these recomendations as,
\begin{equation}
GL (\becquerel/\liter) = \frac{RDL}{DCF \cdot{} q}
\label{eq:Guideline}
\end{equation}
where RDL is the reference dose level in $\sievert/$yr, DCF is the dose conversion factor (the value provided by ICRP for tritium is $1.8 \cdot{} 10^{-11}~\sievert/ \becquerel$ \cite{ICRP_factor}) and $q$ is an estimation of the annual volume of drinking water consumed by a person (normally assumed two liters per day, $730~\liter/$yr). The GL calculated for tritium in drinking water according to the ICRP and WHO recommendations is $76~103~\becquerel/\liter$ and $7~610~\becquerel/\liter$  respectively. This means that tritiated water with activities below these values is considered not harmful for health. Based on these recommendations, each country has created organizations in charge of developing its own legislation limits of exposure to radionuclides. In Spain, the responsible organization of this task is the CSN. Most of the countries in the world implement the RDL of $0.1~\milli\sievert/$yr recommended by the WHO. The legal limit for tritium in drinking water in this case is $7~610~\becquerel/\liter$  but it is often approximated in different ways. Some countries like Switzerland \cite{Switzerland_GL} or some organizations like the WHO \cite{WHO_GL} take this value as $10~000~\becquerel/\liter$. Others like some territories of Canada, such as Ontario and Québec, truncate this value to the first number $7~000~\becquerel/\liter$ \cite{Ontario_GL, Quebec_GL}. There are other countries like Russia which use the much more accurate approximation value of $7~700~\becquerel/\liter$ \cite{Russia_GL}. Other countries like Australia prefer to implement the RDL of $1~\milli\sievert/$yr, recommended by the ICRP, which corresponds to $76~103~\becquerel/\liter$ \cite{Australia_GL}. Finland takes the ICRP recommendations but uses only half of this value, $0.5~\milli\sievert/$yr, rounded to a legal limit of $30~000~\becquerel/\liter$ for tritium in drinking water \cite{Finland_GL}. There are two different exceptions to these recommendations:
\begin{enumerate}
\item{} Most of the USA states like California establish a RDL of $4~\milli\rem~(0.04~\milli\sievert)$, which corresponds to a legal limit of $20~\nano\curie/\liter~(740~\becquerel/\liter)$ \cite{California_GL}. This value was proposed by the United States Environmental Protection Agency (US EPA) as a result of an analysis carried out on the available data. \cite{USEPA_GL}.

\item{} Most of the EU countries, such as France, Germany or Spain, consider a GL of $100~\becquerel/\liter$, which is one of the most restrictive limit in the world \cite{France_GL, Germany_GL, Spain_GL}. This value arise from the consideration that tritium is an indicator of the presence of other radionuclides more dangerous than tritium. These limits are fixed by the EURATOM Council Directive \cite{EURATOM_GL}. 
\end{enumerate}

All limits mentioned in this section are summarized in table \ref{tab:LegalLimitTritium}.

\begin{table}[htbp]
\centering{}%
\begin{tabular}{lc}
\toprule 
Country/Agency & GL ($\becquerel/\liter$) \tabularnewline
\midrule
\midrule 
ICRP & $76~103$ \tabularnewline
WHO & $10~000$ \tabularnewline
Switzerland & $10~000$ \tabularnewline
Canada & $7~000$ \tabularnewline
Russia & $7~700$ \tabularnewline
Australia & $76~103$ \tabularnewline
Finland & $30~000$ \tabularnewline
United States & $740$ \tabularnewline
European Union & $100$ \tabularnewline
\bottomrule
\end{tabular}
\caption{Legal limit of tritium in drinking water (GL) established in several countries.}
\label{tab:LegalLimitTritium}
\end{table}