The aim of the background rejection system is to reduce the radioactive and cosmic background of the TRITIUM monitor. The TRITIUM project follows the ALARA principle for the tritium activity measurement, that is, to measure a tritium activity "as low as reasonably achievable". The detection limit of tritium activity is set by the uncertainty of the background measured by the TRITIUM detector, since tritium activities below this uncertainty cannot be resolved. Therefore, the background must be reduced as much as possible. The total uncertainty is given by the rms of the statistical $\sigma_{st}$ and  systematic $\sigma_{sys}$ uncertainties. Because of the Poissonian nature of the process, the statistical uncertainty is given by the square root of the total activity $A_{m}$ which can be reduced by minimizing the background,
\begin{equation}
\sigma_{T}^2 = \sigma_{st}^2 +\sigma_{sys}^2; \qquad \qquad \sigma_{st} = \sqrt{A_{m}}
\label{eq:SquareSumUncerainty}
\end{equation} 
The background rejection system of the TRITIUM monitor suppresses the background of the TRITIUM detector, reducing the total uncertainty.

The background of TRITIUM has two different sources. On the one hand, the radioactive elements present in the Earth crust, mainly $\ce{^{40}K}$ and elements from the four natural radioactive series, listed in Table \ref{tab:NaturalRadioactiveSeries}. On the other hand, the cosmic ray radiation. The primary cosmic radiation, of extra-terrestrial origin, is composed of high-energy particles, mainly protons and $\alpha$ particles, which interact with the Earth's atmosphere and generate a shower mainly composed of muons, electrons, photons and neutrons. Cosmic radiation depends on several parameters like the longitude, latitude, and the solar activity cycle. The spatial distribution of cosmic rays, mainly muons, follows a $\cos^2\theta$ distribution with the zenith angle $\theta$. 

\begin{table}[htbp]
\centering{}%
\begin{tabular}{lcccc}
\toprule 
Mass Num. & Series & Primary & Half life (y) & Final \tabularnewline
\midrule
\midrule 
4n & Thorium & $\ce{^{232}Th}$ & $1.41 \cdot{} 10^{10}$ & $\ce{^{208}Pb}$ \tabularnewline
4n+1 & Neptunium & $\ce{^{237}Np}$ & $2.14 \cdot{} 10^{6}$ & $\ce{^{209}Pb}$ \tabularnewline
4n+2 & Uranium-Radium & $\ce{^{238}U}$ & $4.51 \cdot{} 10^{9}$ & $\ce{^{206}Pb}$ \tabularnewline
4n+3 & Uranium-Actinium & $\ce{^{235}U}$ & $7.18 \cdot{} 10^{8}$ & $\ce{^{204}Pb}$ \tabularnewline
\bottomrule
\end{tabular}
\caption{Classification of natural radioactive series \cite{NaturalRadioactiveSeries1, NaturalRadioactiveSeries2}. The information displayed for each radioactive series is the name of the series, the primary and final element and the half-life of the primary element.}
\label{tab:NaturalRadioactiveSeries}
\end{table}

Two different techniques are employed for background suppression:

\begin{enumerate}

\item{}  The soft background component, with energy below $200~\MeV$, is stopped by a lead castle.

\item{} The hard background component, with energy greater than $200~\MeV$, is harder to stop and the technique employed is the use of a cosmic veto in anti-coincidence with the TRITIUM detector. 

\end{enumerate}