The objective of this thesis is to design, build and commission an automatic station for real-time monitoring of low tritium activities in water. Its content is mainly focused on the development and optimization of the TRITIUM prototypes and the active veto. This thesis is divided into eight chapters structured as follows:

\begin{enumerate}
\item{} \textbf{Chapter 1} provides a brief introduction to tritium detection, reports some important properties of tritium, and discusses the current legislation that limits tritium levels for human consumption in many countries around the world. 

\item{} \textbf{Chapter 2} describes the state-of-the-art of tritium detection and introduces the TRITIUM project. 

\item{} \textbf{Chapter 3} outlines the different parts of the TRITIUM monitor, which are the tritium detector, the water purification system and the background rejection system (consisting of a lead shield and a active veto). 

\item{} \textbf{Chapter 4} reports the calibrations of the different parts of the TRITIUM monitor and describes the developments aimed at improving the efficiency of tritium detection. 

\item{} \textbf{Chapter 5} details the geometrical configuration of the different prototypes built in the TRITIUM project and the measurements taken with them. 

\item{} \textbf{Chapter 6} details the Monte Carlo simulations performed in the TRITIUM project and shows the results obtained. 

\item{} \textbf{Chapter 7} summarizes and discusses the most important results achieved by the TRITIUM collaboration.

\item{} \textbf{Chapter 8} Summarize the main results of this PhD work and discusses the future of the TRITIUM project.

\end{enumerate}

