Finally, this section shows the results obtained with the simulation of a TRITIUM-IFIC 2 prototype when the background rejection system, detailed in section \ref{subsec:LeadCosmicSimulation}, is included. These simulations quantify the effect on the tritium measurement of both parts of the background rejection system, lead shield and cosmic veto.

Similar to the simulations used for the study of the TRITIUM-IFIC 2 prototype, analogous variables were used as tests, which were systematically verified, to ensure that all the steps of the simulations were carried out correctly.

Three different simulations were carried out to independently quantify how the tritium detection is affected due to both, the lead shield and the cosmic veto. The first simulation consists of a TRITIUM-IFIC 2 prototype and the cosmic ray source, in the second simulation a lead shield was added and for the third simulation, the cosmic veto was also included.

The cosmic events detected by the TRITIUM-IFIC 2 prototype are reduced around 5.5 times when a lead shielding with walls of $5~\cm$ is included. This reduction is mainly caused due to the stop of the weak cosmic radiation (energy lower than $200~\MeV$). It has to be taken into account that the natural backgrounds of the place are not included in this simulation. This radioactive background will be also stopped by the lead shielding, so the expected reduction of the radioactive background due to the passive veto is even better.

Regarding to the cosmic events that pass through the lead shield and reach the TRITIUM IFIC 2 prototype, which are the hard cosmic radiation, a percentage of around $10\%$ is detected with the cosmic veto and, therefore, removed to the tritium measurement.

Therefore, the usefulness of both parties of the background rejection system, lead shield and active veto, has been demonstrated by quantifying their effect.